\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-05 paper/draft.tex
Add a paragraph on the complete annotation language and the annotation records that we have written and remove the appendix

\heading{Custom Aggregators}
For commands in \sta, the annotations are enough to enable parallelization:
  commands are applied to parts of their input in parallel, and their outputs are simply concatenated.
%% commands either fall under \sta, having straightforward aggregators, or fall under a subset of \pur that can be parallelized using divide-and-conquer techniques~\sx{optimizer}. \kk{pure commands are what we have to provide aggregators for, so this is not totally valid.}
%% Unfortunately, there are commands that
%% require less obvious tactics---after all, \unix commands are Turing-complete programs and failing to plan for this generality would inhibit \sys's usefulness. \kk{I would propose deleting this last sentence. we have already separated commands into classes, so this sentence makes it seem like the classes don't help at all.}
%
To support the parallelization of arbitrary commands in \pur, \sys allows supplying custom \emph{map} and \emph{aggregate} functions.
In line with the \unix philosophy, these functions can be written in any language as long as they conform to a few invariants:
  (i) \emph{map} is in \sta and \emph{aggregate} is in \pur,
  (ii) \emph{map} can consume (or extend) the output of the original command and  \emph{aggregate} can consume (and combine) the results of multiple \emph{map} invocations, and
  (iii) their composition produces the same output as the original command.
If these invariants are met, after DFG analysis~\sx{ir} \sys can replace occurrences of these commands with their \emph{map} and \emph{aggregate} equivalents, enabling their full parallelization.

\heading{Annotation Effort}
%
\sys defines aggregators for many POSIX and GNU commands in \pur, dubbing as both its standard library and an exemplar for community efforts tackling other commands.
\str
% \kk{We should mention somewhere that we used the language to annotate N commands.} 
% \kk{Mention that some commands, such as xargs are handled internally due to their particularities.}

@@

\appendix

\section{Annotation Language Grammar}
\label{alg}

\Cref{fig:dsl} shows the complete grammar of the parallelizability
annotation language.

\begin{figure}
  \centering
  \begin{grammar}
    <option> ::= `-' <string>

    <category> ::= `stateless' | `pure' | ...

    <maybe-int> ::= | <int>

    <arg> ::= `args[' <int> `]'

    <args> ::= <arg>
    \alt `args[' <maybe-int> `:' <maybe-int> `]'

    <input> ::= `stdin' | <args>

    <inputs> ::= <input>
    \alt <input> `,' <inputs>

    <output> ::= `stdout' | <arg>

    <outputs> ::= <output>
    \alt <output> `,' <outputs>

    <option-pred> ::= <option>
    \alt `value' <option> = <string>
    \alt `not' <option-pred>
    \alt <option-pred> `or' <option-pred>
    \alt <option-pred> `and' <option-pred>

    <assignment> ::= `(' <category>, `[' <inputs> `]' `,' `[' <output> `]' `)'

    <predicate> ::= <option-pred> `=>' <assignment>

    <pred-list> ::= `|' <predicate> <pred-list>
    \alt `|' `otherwise' `=>' <assignment>

    <command> ::= <name> `\{' <pred-list> `\}'

    <command-list> ::= <command>
    \alt <command> <command-list>
  \end{grammar}
  \caption{
  \textbf{Parallelizability description language.}
    The DSL captures important information regarding the parallelizability of a command.
  }
  \label{fig:dsl}
\end{figure}

>>>>

\heading{Complete Annotation Language}
%
The complete annotation language contains 6 operators (one of which supports regural expressions), and we used it to specify the annotation records for \todo{X} commands---an effort that took about \todo{N} hours. An important point is that annotation records can be conservative by default to not jeopardize correctness, but can be incrementally refined to capture parallelizability when using combinations of flags. Our language is extensible with more operators (as long as the user defines an interpreter for them) and also supports writing arbitrary python code for commands whose properties are difficult to capture, such as the higher order \ttt{xargs} whose parallelizability class depends on the class of the command that it invokes.
% \str
% \kk{Mention that some commands, such as xargs are handled internally due to their particularities.}

\heading{Custom Aggregators}
For commands in \sta, the annotations are enough to enable parallelization:
  commands are applied to parts of their input in parallel, and their outputs are simply concatenated.
%% commands either fall under \sta, having straightforward aggregators, or fall under a subset of \pur that can be parallelized using divide-and-conquer techniques~\sx{optimizer}. \kk{pure commands are what we have to provide aggregators for, so this is not totally valid.}
%% Unfortunately, there are commands that
%% require less obvious tactics---after all, \unix commands are Turing-complete programs and failing to plan for this generality would inhibit \sys's usefulness. \kk{I would propose deleting this last sentence. we have already separated commands into classes, so this sentence makes it seem like the classes don't help at all.}
%
To support the parallelization of arbitrary commands in \pur, \sys allows supplying custom \emph{map} and \emph{aggregate} functions.
In line with the \unix philosophy, these functions can be written in any language as long as they conform to a few invariants:
  (i) \emph{map} is in \sta and \emph{aggregate} is in \pur,
  (ii) \emph{map} can consume (or extend) the output of the original command and  \emph{aggregate} can consume (and combine) the results of multiple \emph{map} invocations, and
  (iii) their composition produces the same output as the original command.
\sys can use the \emph{map} and \emph{aggregate} functions in its graph transformations~\sx{ir} to further expose parallelism.
% If these invariants are met, after DFG analysis~\sx{ir} \sys can replace occurrences of these commands with their \emph{map} and \emph{aggregate} equivalents, enabling their full parallelization.
\sys defines aggregators for many POSIX and GNU commands in \pur, dubbing as both its standard library and an exemplar for community efforts tackling other commands.

@@

% \appendix

% \section{Annotation Language Grammar}
% \label{alg}

% \Cref{fig:dsl} shows the complete grammar of the parallelizability
% annotation language.

% \begin{figure}
%   \centering
%   \begin{grammar}
%     <option> ::= `-' <string>

%     <category> ::= `stateless' | `pure' | ...

%     <maybe-int> ::= | <int>

%     <arg> ::= `args[' <int> `]'

%     <args> ::= <arg>
%     \alt `args[' <maybe-int> `:' <maybe-int> `]'

%     <input> ::= `stdin' | <args>

%     <inputs> ::= <input>
%     \alt <input> `,' <inputs>

%     <output> ::= `stdout' | <arg>

%     <outputs> ::= <output>
%     \alt <output> `,' <outputs>

%     <option-pred> ::= <option>
%     \alt `value' <option> = <string>
%     \alt `not' <option-pred>
%     \alt <option-pred> `or' <option-pred>
%     \alt <option-pred> `and' <option-pred>

%     <assignment> ::= `(' <category>, `[' <inputs> `]' `,' `[' <output> `]' `)'

%     <predicate> ::= <option-pred> `=>' <assignment>

%     <pred-list> ::= `|' <predicate> <pred-list>
%     \alt `|' `otherwise' `=>' <assignment>

%     <command> ::= <name> `\{' <pred-list> `\}'

%     <command-list> ::= <command>
%     \alt <command> <command-list>
%   \end{grammar}
%   \caption{
%   \textbf{Parallelizability description language.}
%     The DSL captures important information regarding the parallelizability of a command.
%   }
%   \label{fig:dsl}
% \end{figure}
